\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-05 introduction.tex
baby steps

>>>>

It is hard to write modular, extensible code.
It is even harder to write modular, extensible proofs.
While there exist many linguistic solutions to code reuse and
extensibility in object-oriented and functional languages,
linguistic solutions are lacking in proof assistants.

Meanwhile, language designers and researchers are increasingly
using proof assistants to mechanize meta\-theories, building on each
other's work.
Therefore, it has become ever more important that proof assistants
make it easy to write reusable, extensible code and proofs.
